Variants of G\"{o}del's Ontological Proof \\ in a Natural Deduction Calculus

### 2016-09-08 Papers/InProgress/NaturalDeduction/GodProof-ND.tex
checking from section 6. Part 2.
Move equality rules

The calculus having only the rules shown in Figures \ref{fig:PropositionalRules}, \ref{fig:Classical} and \ref{fig:QuantifierRules} is named \ND, while the calculus with the additional rules shown in Figure \ref{fig:NDK} is named \NDK.

@@

\begin{small}
\begin{prooftree}
\AXC{$ $} \RightLabel{2}
\UIC{$\neg P(\rho)$} 
\AXC{Axiom 1} \dashedLine
\UIC{$\all \varphi. [P(\neg \varphi) \biimp \neg P(\varphi)]$} \RightLabel{$\all_E$}
\UIC{$P(\lambda x. \neg \rho(x)) \biimp \neg P(\rho)$} \RightLabel{$\wedge_E$}
\UIC{$\neg P(\rho) \imp P(\lambda x. \neg \rho(x))$}\RightLabel{$\imp_E$}
\BIC{$P(\lambda x. \neg \rho(x))$}
\AXC{$ $} \RightLabel{1}
\UIC{$\ex z. G(z)$}\RightLabel{$\ex_E$}
\UIC{$G(\gamma)$}  \dottedLine \RightLabel{D\ref{N:D1}}
\UIC{$\forall \varphi.(P(\varphi) \imp \varphi(\gamma))$}\RightLabel{$\forall_E$}
\UIC{$P(\lambda x. \neg \rho(x)) \imp \neg \rho(\gamma)$}\RightLabel{$\imp_E$}
\BIC{$\neg \rho(\gamma)$}
\AXC{$ $} \RightLabel{3}
\UIC{$\rho(\gamma)$} \RightLabel{$\imp_E$}
\BIC{$\bot$}\RightLabel{$\imp_I^2$}
\UIC{$\neg\neg P(\rho)$}\RightLabel{$\neg\neg_E$}
\UIC{$[\subproof_7] \qquad P(\rho)$}
\end{prooftree}
\end{small}

@@

%\AXC{$ $} \RightLabel{6}
%\UIC{$\rho(\gamma)$} \RightLabel{}
\AXC{$ \subproof_7$} \dashedLine
\UIC{$P(\rho)$} %\RightLabel{$\nec_E$}
\AXC{Axiom \ref{N:A4}} \dashedLine
\UIC{$\all \varphi.[P(\varphi) \imp \nec\; P(\varphi)]$}\RightLabel{$\forall_E$}
\UIC{$P(\rho) \imp \nec\; P(\rho)$}\RightLabel{$\imp_E$}
\BIC{$\nec P(\rho)$}\RightLabel{$\imp_E$}%\RightLabel{$\imp_I^3$}
%\UIC{$[\subproof_7] \qquad \rho(\gamma) \imp \nec\; P(\rho)$}
%\UIC{$\rho(\gamma)\imp\Box P(\rho)$}\RightLabel{$\imp_E$}
%\BIC{$\nec P(\rho)$} \RightLabel{$\imp_E$}

\BIC{$\nec \forall y .(G(y)\imp \rho(y))$}\RightLabel{$\imp_I^6$}
\UIC{$\rho(\gamma) \imp \nec \forall y.(G(y) \imp \rho(y))$}\RightLabel{$\forall_I$}
\UIC{$\forall \psi.(\psi(\gamma) \imp \nec \forall y.(G(y) \imp \psi(y)))$}
\AXC{$ $} \RightLabel{1}
\UIC{$\ex z. G(z)$}\RightLabel{$\ex_E$}
\UIC{$G(\gamma)$}  \RightLabel{$\wedge_I$}
\BIC{$G(\gamma) \wedge \forall \psi.(\psi(\gamma) \imp \nec \forall y.(G(y) \imp \psi(y)))$}\dottedLine \RightLabel{D\ref{N:D2}}
\UIC{$[\subproof_8] \qquad \ess{G}{\gamma}$}
\end{prooftree}
\end{small}

\begin{small}
\begin{prooftree}
\AXC{$\subproof_8$} \dashedLine
\UIC{$\ess{G}{\gamma}$}
\AXC{Axiom \ref{A5}} \dashedLine
\UIC{$P(E)$}\dottedLine 
\AXC{$ $} \RightLabel{1}
\UIC{$\ex z. G(z)$}\RightLabel{$\ex_E$}
\UIC{$G(\gamma)$}\dottedLine \RightLabel{D\ref{N:D1}}
\UIC{$\forall \varphi.(P(\varphi) \imp \varphi(\gamma))$}\RightLabel{$\forall_E$}
\UIC{$P(E) \imp E(\gamma)$}\RightLabel{$\imp_E$}
\BIC{$E(\gamma)$}\dottedLine \RightLabel{D\ref{N:D3}}
\UIC{$ \all \varphi.[\ess{\varphi}{\gamma} \imp \nec \ex x.\varphi(x)] $}\RightLabel{$\all_E$}
\UIC{$ \ess{G}{\gamma} \imp \nec \ex x. G(x) $}\RightLabel{$\imp_E$}
\BIC{$\nec \ex x. G(x)$} \RightLabel{$\imp_I^1$}
\UIC{$\ex z. G(z) \imp \nec \ex x. G(x)$}
\end{prooftree}
\end{small}
\end{proof}

@@

\begin{small}
\begin{prooftree}
\AXC{Theorem 2}\dashedLine
\UIC{$\all y.[G(y) \imp \ess{G}{y}]$} \RightLabel{D2 }\dottedLine
\UIC{$\all y.[G(y) \imp G(y) \wedge \all \psi. (\psi(y) \imp \nec \all x. (G(x) \imp \psi(x)))]$}\doubleLine
\UIC{$\all y.[G(y) \imp \all \psi. (\psi(y) \imp \nec \all x. (G(x) \imp \psi(x)))]$} \doubleLine
%\UIC{$\all y.[G(y) \imp (A(y) \imp \nec \all x. (G(x) \imp A(x)))]$} \RightLabel{$A$ is constant}
\UIC{$\all y.[G(y) \imp (A \imp \nec \all x. (G(x) \imp A))]$} \doubleLine
\UIC{$[\subproof_9] \qquad \ex y.G(y) \imp (A \imp \nec \all x. (G(x) \imp A))$}
\end{prooftree}
\end{small}

\begin{small}
\begin{prooftree}
\AXC{$ \subproof_9 $}\dashedLine
\UIC{$\ex y.G(y) \imp (A \imp \nec \all x. (G(x) \imp A))$}
\AXC{Theorem 3}\dashedLine
\UIC{$\nec \ex y.G(y)$} \RightLabel{$\nec_E$}
\UIC{$\ex y.G(y)$} \RightLabel{$\imp_E$}
\BIC{$ A \imp \nec \all x. (G(x) \imp A)$} \doubleLine
\UIC{$ A \imp \nec (\ex x. G(x) \imp A)$}
\AXC{$ $} \RightLabel{1}
\UIC{$A$} \RightLabel{$\imp_E$}
\BIC{$ \nec (\ex x. G(x) \imp A)$} \RightLabel{$\nec_E$}
\UIC{$ \omega:  \ex x. G(x) \imp A$} \RightLabel{$\imp_E$}
\AXC{Theorem 3}\dashedLine
\UIC{$\nec \ex y.G(y)$} \RightLabel{$\nec_E$}
\UIC{$\omega: \ex x.G(x)$} \RightLabel{$\imp_E$}
\BIC{$\omega: A$} \RightLabel{$\nec_I$}
\UIC{$ \nec A$} \RightLabel{$\imp_I^1$}
   \UIC{$A\imp \nec A$}
\end{prooftree}
\end{small}

@@

\begin{lemma}
\label{A:L1}
If there is a God-like being, then there is a God-like being necessarily:
$$
\ex z. G(z) \imp \nec \ex x. G(x)
$$
\end{lemma}
\begin{proof} \hfill
\begin{prooftree}
\AXC{$ $} \RightLabel{1}
\UIC{$\ex z. G(z)$}\RightLabel{$\ex_E$}
\UIC{$[\subproof_6] \quad G(\gamma)$}
\end{prooftree}

\begin{prooftree}
\AXC{$\subproof_6$} \dashedLine
\UIC{$G(\gamma)$} \RightLabel{}\dottedLine \RightLabel{D\ref{A:D1}}
\UIC{$\forall \varphi. [P(\lambda x.\varphi(x)) \biimp \nec \varphi(\gamma)]$}\RightLabel{$\forall_E$}
\UIC{$P(\lambda x.\rho(x)) \biimp \nec \rho(\gamma)$}
\AXC{$ $} \RightLabel{4}
\UIC{$\nec\rho(\gamma)$} \RightLabel{$\biimp_E$}
\BIC{$P(\rho)$} \RightLabel{$\forall_E$}

\AXC{Axiom \ref{A:A4}} \dashedLine
\UIC{$P(\rho)\imp \nec P(\rho)$} \RightLabel{$\imp_E$}
\BIC{$[\subproof_7] \quad \nec P(\rho)$} \RightLabel{$\imp_E$}
\end{prooftree}

@@

\AXC{$\subproof_7$} \dashedLine
\UIC{$\nec P(\rho)$}\RightLabel{$\imp_E$}
\BIC{$\nec \forall y .(G(y)\imp \rho(y))$}\RightLabel{$\imp_I^4$}
\UIC{$[\subproof_8] \qquad \nec\rho(\gamma) \imp \nec \forall y.(G(y) \imp \rho(y))$}\RightLabel{$\forall_I$}
\end{prooftree}

%implication for equivalence in essence: 
%\begin{small}
\begin{prooftree}
\AXC{Axiom \ref{A:A3}} \dashedLine
\UIC{$P(G)$}
\AXC{$ $} \RightLabel{5}
\UIC{$\nec  \forall y. [G(y)\imp \varphi(y)]$}\RightLabel{$\wedge_I$}
\BIC{$P(G)\wedge \nec  \forall y. [G(y)\imp \varphi(y)]$}\RightLabel{$\imp_E$}
\AXC{Axiom \ref{A:A2}} 
\BIC{$P(\varphi)$}
\AXC{$\subproof_6$} \dashedLine 
\UIC{$  G(\gamma)$}  \RightLabel{D\ref{A:D1}}
\UIC{$ \all \varphi. [P(\varphi)\biimp \nec \varphi(\gamma)]$}  \RightLabel{$\all_E$}
\UIC{$ P(\varphi)\biimp \nec \varphi(\gamma)$}  \RightLabel{$\biimp_E$}
\BIC{$ \nec \varphi(\gamma)$} \RightLabel{$\imp_I^5$}
\UIC{$[\subproof_9] \quad \nec  \forall y. [G(y)\imp \varphi(y)]\imp \nec \varphi(\gamma)$}
\end{prooftree}
%\end{small}

\begin{small}
\begin{prooftree}
\AXC{$\subproof_8$ and $\subproof_9$} \dashedLine
\UIC{$\nec \varphi(\gamma)\biimp \nec  \forall y. [G(y)\imp \varphi(y)] $} \RightLabel{$\forall_I$}
\UIC{$\forall \varphi. (\nec \varphi(\gamma)\biimp \nec  \forall y. [G(y)\imp \varphi(y)]) $}
\AXC{$ \subproof_6 $} \dashedLine
\UIC{$G(\gamma)$}\RightLabel{$\wedge_I$}
\BIC{$\ess{G}{\gamma}$}
\AXC{Axiom \ref{A5}} \dashedLine
\UIC{$P(E)$}\dottedLine 
\AXC{$\subproof_6$} \dashedLine
\UIC{$G(\gamma)$}\dottedLine \RightLabel{D\ref{A:D1}}
\UIC{$\forall \varphi.(P(\varphi) \biimp \nec \varphi(\gamma))$}\RightLabel{$\forall_E$}
\UIC{$P(E) \biimp \nec E(\gamma)$}\RightLabel{$\biimp_E$}
\BIC{$\nec E(\gamma)$}\RightLabel{$\nec_E$}
   % \AXC{Axiom T} \dashedLine
    %\UIC{$\nec E(\gamma) \imp E(\gamma)$} \RightLabel{$\imp_E$}
\UIC{$ E(\gamma)$} \dottedLine \RightLabel{D\ref{A:D3}}
\UIC{$ \all \varphi.[\ess{\varphi}{\gamma} \imp \nec \ex x.\varphi(x)] $}\RightLabel{$\all_E$}
\UIC{$ \ess{G}{\gamma} \imp \nec \ex x. G(x) $}\RightLabel{$\imp_E$}
\BIC{$\nec \ex x. G(x)$} \RightLabel{$\imp_I^1$}
\UIC{$\ex z. G(z) \imp \nec \ex x. G(x)$}
\end{prooftree}
\end{small}
%\end{tiny}
\end{proof}

@@

\begin{proof} \hfill
\begin{prooftree}
\AXC{$ $} \RightLabel{1}
\UIC{$\ex z. G(z)$}\RightLabel{$\ex_E$}
\UIC{$[\subproof_6] \quad G(\gamma)$}
\end{prooftree}

%\begin{scriptsize}
\begin{prooftree}
\AXC{$\subproof_6$} \dashedLine
\UIC{$G(\gamma)$}  \dottedLine \RightLabel{D\ref{D1}}
\UIC{$\forall \varphi. [P(\lambda x.\varphi(x)) \biimp \nec \varphi(\gamma)]$}\RightLabel{$\forall_E$}
\UIC{$P(G) \biimp \nec G(\gamma)$}
\AXC{Axiom \ref{A:A3}} \RightLabel{}
\UIC{$P(G)$} \RightLabel{$\biimp_E$}
\BIC{$\nec G(\gamma)$}
\AXC{$ $} \RightLabel{2}
\UIC{$G(\gamma)$} \RightLabel{$\ex_I$}
\UIC{$\ex x.G(x)$}  \RightLabel{$\imp_I^2$}
\UIC{$G(\gamma)\imp \ex x.G(x)$} \RightLabel{$\nec_I$}
\UIC{$\nec [G(\gamma)\imp \ex x.G(x)]$} \doubleLine  \RightLabel{(Axiom K)}
\UIC{$\nec G(\gamma)\imp \nec \ex x.G(x)$} \RightLabel{$\imp_E$}
\BIC{$\nec \ex x.G(x)$}\RightLabel{$\imp_I^1$}
\UIC{$\ex z. G(z)\imp \nec \ex x.G(x)$}
\end{prooftree}
%\end{scriptsize}

@@

\begin{small}
\begin{prooftree}
\AXC{Theorem 2}\dashedLine
\UIC{$\all y.[G(y) \imp \ess{G}{y}]$} \RightLabel{D2 }\doubleLine
\UIC{$\all y.[G(y) \imp G(y) \wedge \all \psi. (\nec \psi(y) \biimp \nec \all x. (G(x) \imp \psi(x)))]$}
\UIC{$\all y.[G(y) \imp \all \psi. (\nec \psi(y) \biimp \nec \all x. (G(x) \imp \psi(x)))]$} \doubleLine
%\UIC{$\all y.[G(y) \imp (\nec A(y) \biimp \nec \all x. (G(x) \imp A(x)))]$} \RightLabel{$A$ is constant}
\UIC{$\all y.[G(y) \imp (\nec A \biimp \nec \all x. (G(x) \imp A))]$} \doubleLine
\UIC{$[\subproof_{10}] \qquad \ex y.G(y) \imp (\nec A \biimp \nec \all x. (G(x) \imp A))$}
\end{prooftree}
\end{small}

\begin{small}
\begin{prooftree}
\AXC{$ \subproof_{10} $}\dashedLine
\UIC{$\ex y.G(y) \imp (\nec A \biimp \nec \all x. (G(x) \imp A))$}
\AXC{Theorem 3}\dashedLine
\UIC{$\nec \ex y.G(y)$} \RightLabel{$\nec_E$}
\UIC{$\ex y.G(y)$} \RightLabel{$\imp_E$}
\BIC{$ \nec A \biimp \nec \all x. (G(x) \imp A)$} \doubleLine
\UIC{$ \nec A \biimp \nec (\ex x. G(x) \imp A)$}
\AXC{$ $} \RightLabel{1}
\UIC{$\nec A$} \RightLabel{$\imp_E$}
\BIC{$ \nec (\ex x. G(x) \imp A)$} \RightLabel{$\nec_E$}
\UIC{$ \omega:  \ex x. G(x) \imp A$} %\RightLabel{$\imp_E$}
\AXC{Theorem 3}\dashedLine
\UIC{$\nec \ex y.G(y)$} \RightLabel{$\nec_E$}
\UIC{$\omega: \ex x.G(x)$} \RightLabel{$\imp_E$}
\BIC{$\omega: A$} \RightLabel{$\nec_I$}
\UIC{$ \nec A$} \RightLabel{$\imp_I^1$}
   \UIC{$\nec A\imp \nec A$}
\end{prooftree}
\end{small}

@@

\begin{lemma}
\label{B:L1}
If there is a God-like being, then there is a God-like being necessarily:
$$
\ex z. G_B(z) \imp \nec \ex x. G_B(x)
$$
\end{lemma}
\begin{proof}\hfill
\begin{small}
\begin{prooftree}
\AXC{$ $} \RightLabel{$2$}
\UIC{$G_B(x) $} 
\AXC{$ $}\doubleLine
\UIC{$\nec \all x. [G_B(x) \imp G_B(x)] $}\RightLabel{ D\ref{B:D1}}\dottedLine
\UIC{$P_B(G_B) $}\RightLabel{ $\wedge_I$}
\BIC{$[\subproof_{11}] \qquad G_B(x) \wedge P_B(G_B) $}
\end{prooftree}
\end{small}

>>>>

The calculus having only the rules shown in Figures \ref{fig:PropositionalRules}, \ref{fig:Classical}, \ref{fig:QuantifierRules} and \ref{fig:EqualityRules} is named \ND, while the calculus with the additional rules shown in Figure \ref{fig:NDK} is named \NDK.

@@

\begin{small}
\begin{prooftree}
\AXC{$ $} \RightLabel{2}
\UIC{$\neg P(\rho)$} 
\AXC{Axiom 1} \dashedLine
\UIC{$\all \varphi. [P(\neg \varphi) \biimp \neg P(\varphi)]$} \RightLabel{$\all_E$}
\UIC{$P(\lambda x. \neg \rho(x)) \biimp \neg P(\rho)$} \RightLabel{$\wedge_E$}
\UIC{$\neg P(\rho) \imp P(\lambda x. \neg \rho(x))$}\RightLabel{$\imp_E$}
\BIC{$P(\lambda x. \neg \rho(x))$}
\AXC{$ $} \RightLabel{1}
\UIC{$\ex z. G(z)$}\RightLabel{$\ex_E$}
\UIC{$G(\gamma)$}  \dottedLine \RightLabel{D\ref{N:D1}}
\UIC{$\forall \varphi.(P(\varphi) \imp \varphi(\gamma))$}\RightLabel{$\forall_E$}
\UIC{$P(\lambda x. \neg \rho(x)) \imp \neg \rho(\gamma)$}\RightLabel{$\imp_E$}
\BIC{$\neg \rho(\gamma)$}
\AXC{$ $} \RightLabel{3}
\UIC{$\rho(\gamma)$} \RightLabel{$\imp_E$}
\BIC{$\bot$}\RightLabel{$\imp_I^2$}
\UIC{$\neg\neg P(\rho)$}\RightLabel{$\neg\neg_E$}
\UIC{$[\subproof_6] \qquad P(\rho)$}
\end{prooftree}
\end{small}

@@

%\AXC{$ $} \RightLabel{6}
%\UIC{$\rho(\gamma)$} \RightLabel{}
\AXC{$ \subproof_6$} \dashedLine
\UIC{$P(\rho)$} %\RightLabel{$\nec_E$}
\AXC{Axiom \ref{N:A4}} \dashedLine
\UIC{$\all \varphi.[P(\varphi) \imp \nec\; P(\varphi)]$}\RightLabel{$\forall_E$}
\UIC{$P(\rho) \imp \nec\; P(\rho)$}\RightLabel{$\imp_E$}
\BIC{$\nec P(\rho)$}\RightLabel{$\imp_E$}%\RightLabel{$\imp_I^3$}
%\UIC{$[\subproof_7] \qquad \rho(\gamma) \imp \nec\; P(\rho)$}
%\UIC{$\rho(\gamma)\imp\Box P(\rho)$}\RightLabel{$\imp_E$}
%\BIC{$\nec P(\rho)$} \RightLabel{$\imp_E$}

\BIC{$\nec \forall y .(G(y)\imp \rho(y))$}\RightLabel{$\imp_I^6$}
\UIC{$\rho(\gamma) \imp \nec \forall y.(G(y) \imp \rho(y))$}\RightLabel{$\forall_I$}
\UIC{$\forall \psi.(\psi(\gamma) \imp \nec \forall y.(G(y) \imp \psi(y)))$}
\AXC{$ $} \RightLabel{1}
\UIC{$\ex z. G(z)$}\RightLabel{$\ex_E$}
\UIC{$G(\gamma)$}  \RightLabel{$\wedge_I$}
\BIC{$G(\gamma) \wedge \forall \psi.(\psi(\gamma) \imp \nec \forall y.(G(y) \imp \psi(y)))$}\dottedLine \RightLabel{D\ref{N:D2}}
\UIC{$[\subproof_7] \qquad \ess{G}{\gamma}$}
\end{prooftree}
\end{small}

\begin{small}
\begin{prooftree}
\AXC{$\subproof_7$} \dashedLine
\UIC{$\ess{G}{\gamma}$}
\AXC{Axiom \ref{A5}} \dashedLine
\UIC{$P(E)$}\dottedLine 
\AXC{$ $} \RightLabel{1}
\UIC{$\ex z. G(z)$}\RightLabel{$\ex_E$}
\UIC{$G(\gamma)$}\dottedLine \RightLabel{D\ref{N:D1}}
\UIC{$\forall \varphi.(P(\varphi) \imp \varphi(\gamma))$}\RightLabel{$\forall_E$}
\UIC{$P(E) \imp E(\gamma)$}\RightLabel{$\imp_E$}
\BIC{$E(\gamma)$}\dottedLine \RightLabel{D\ref{N:D3}}
\UIC{$ \all \varphi.[\ess{\varphi}{\gamma} \imp \nec \ex x.\varphi(x)] $}\RightLabel{$\all_E$}
\UIC{$ \ess{G}{\gamma} \imp \nec \ex x. G(x) $}\RightLabel{$\imp_E$}
\BIC{$\nec \ex x. G(x)$} \RightLabel{$\imp_I^1$}
\UIC{$\ex z. G(z) \imp \nec \ex x. G(x)$}
\end{prooftree}
\end{small}
\end{proof}

@@

\begin{small}
\begin{prooftree}
\AXC{Theorem 2}\dashedLine
\UIC{$\all y.[G(y) \imp \ess{G}{y}]$} \RightLabel{D2 }\dottedLine
\UIC{$\all y.[G(y) \imp G(y) \wedge \all \psi. (\psi(y) \imp \nec \all x. (G(x) \imp \psi(x)))]$}\doubleLine
\UIC{$\all y.[G(y) \imp \all \psi. (\psi(y) \imp \nec \all x. (G(x) \imp \psi(x)))]$} \doubleLine
%\UIC{$\all y.[G(y) \imp (A(y) \imp \nec \all x. (G(x) \imp A(x)))]$} \RightLabel{$A$ is constant}
\UIC{$\all y.[G(y) \imp (A \imp \nec \all x. (G(x) \imp A))]$} \doubleLine
\UIC{$[\subproof_8] \qquad \ex y.G(y) \imp (A \imp \nec \all x. (G(x) \imp A))$}
\end{prooftree}
\end{small}

\begin{small}
\begin{prooftree}
\AXC{$ \subproof_8 $}\dashedLine
\UIC{$\ex y.G(y) \imp (A \imp \nec \all x. (G(x) \imp A))$}
\AXC{Theorem 3}\dashedLine
\UIC{$\nec \ex y.G(y)$} \RightLabel{$\nec_E$}
\UIC{$\ex y.G(y)$} \RightLabel{$\imp_E$}
\BIC{$ A \imp \nec \all x. (G(x) \imp A)$} \doubleLine
\UIC{$ A \imp \nec (\ex x. G(x) \imp A)$}
\AXC{$ $} \RightLabel{1}
\UIC{$A$} \RightLabel{$\imp_E$}
\BIC{$ \nec (\ex x. G(x) \imp A)$} \RightLabel{$\nec_E$}
\UIC{$ \omega:  \ex x. G(x) \imp A$} \RightLabel{$\imp_E$}
\AXC{Theorem 3}\dashedLine
\UIC{$\nec \ex y.G(y)$} \RightLabel{$\nec_E$}
\UIC{$\omega: \ex x.G(x)$} \RightLabel{$\imp_E$}
\BIC{$\omega: A$} \RightLabel{$\nec_I$}
\UIC{$ \nec A$} \RightLabel{$\imp_I^1$}
   \UIC{$A\imp \nec A$}
\end{prooftree}
\end{small}

@@

\begin{lemma}
\label{A:L1}
If there is a God-like being, then there is a God-like being necessarily:
$$
\ex z. G(z) \imp \nec \ex x. G(x)
$$
\end{lemma}
\begin{proof} \hfill
\begin{prooftree}
\AXC{$ $} \RightLabel{1}
\UIC{$\ex z. G(z)$}\RightLabel{$\ex_E$}
\UIC{$[\subproof_9] \quad G(\gamma)$}
\end{prooftree}

\begin{prooftree}
\AXC{$\subproof_9$} \dashedLine
\UIC{$G(\gamma)$} \RightLabel{}\dottedLine \RightLabel{D\ref{A:D1}}
\UIC{$\forall \varphi. [P(\lambda x.\varphi(x)) \biimp \nec \varphi(\gamma)]$}\RightLabel{$\forall_E$}
\UIC{$P(\lambda x.\rho(x)) \biimp \nec \rho(\gamma)$}
\AXC{$ $} \RightLabel{4}
\UIC{$\nec\rho(\gamma)$} \RightLabel{$\biimp_E$}
\BIC{$P(\rho)$} \RightLabel{$\forall_E$}

\AXC{Axiom \ref{A:A4}} \dashedLine
\UIC{$P(\rho)\imp \nec P(\rho)$} \RightLabel{$\imp_E$}
\BIC{$[\subproof_{10}] \quad \nec P(\rho)$} \RightLabel{$\imp_E$}
\end{prooftree}

@@

\AXC{$\subproof_{10}$} \dashedLine
\UIC{$\nec P(\rho)$}\RightLabel{$\imp_E$}
\BIC{$\nec \forall y .(G(y)\imp \rho(y))$}\RightLabel{$\imp_I^4$}
\UIC{$[\subproof_{11}] \qquad \nec\rho(\gamma) \imp \nec \forall y.(G(y) \imp \rho(y))$}\RightLabel{$\forall_I$}
\end{prooftree}

%implication for equivalence in essence: 
%\begin{small}
\begin{prooftree}
\AXC{Axiom \ref{A:A3}} \dashedLine
\UIC{$P(G)$}
\AXC{$ $} \RightLabel{5}
\UIC{$\nec  \forall y. [G(y)\imp \varphi(y)]$}\RightLabel{$\wedge_I$}
\BIC{$P(G)\wedge \nec  \forall y. [G(y)\imp \varphi(y)]$}\RightLabel{$\imp_E$}
\AXC{Axiom \ref{A:A2}} 
\BIC{$P(\varphi)$}
\AXC{$\subproof_9$} \dashedLine 
\UIC{$  G(\gamma)$}  \RightLabel{D\ref{A:D1}}
\UIC{$ \all \varphi. [P(\varphi)\biimp \nec \varphi(\gamma)]$}  \RightLabel{$\all_E$}
\UIC{$ P(\varphi)\biimp \nec \varphi(\gamma)$}  \RightLabel{$\biimp_E$}
\BIC{$ \nec \varphi(\gamma)$} \RightLabel{$\imp_I^5$}
\UIC{$[\subproof_{12}] \quad \nec  \forall y. [G(y)\imp \varphi(y)]\imp \nec \varphi(\gamma)$}
\end{prooftree}
%\end{small}

\begin{small}
\begin{prooftree}
\AXC{$\subproof_{11}$ and $\subproof_{12}$} \dashedLine
\UIC{$\nec \varphi(\gamma)\biimp \nec  \forall y. [G(y)\imp \varphi(y)] $} \RightLabel{$\forall_I$}
\UIC{$\forall \varphi. (\nec \varphi(\gamma)\biimp \nec  \forall y. [G(y)\imp \varphi(y)]) $}
\AXC{$ \subproof_{9}$} \dashedLine
\UIC{$G(\gamma)$}\RightLabel{$\wedge_I$}
\BIC{$\ess{G}{\gamma}$}
\AXC{Axiom \ref{A5}} \dashedLine
\UIC{$P(E)$}\dottedLine 
\AXC{$\subproof_9$} \dashedLine
\UIC{$G(\gamma)$}\dottedLine \RightLabel{D\ref{A:D1}}
\UIC{$\forall \varphi.(P(\varphi) \biimp \nec \varphi(\gamma))$}\RightLabel{$\forall_E$}
\UIC{$P(E) \biimp \nec E(\gamma)$}\RightLabel{$\biimp_E$}
\BIC{$\nec E(\gamma)$}\RightLabel{$\nec_E$}
   % \AXC{Axiom T} \dashedLine
    %\UIC{$\nec E(\gamma) \imp E(\gamma)$} \RightLabel{$\imp_E$}
\UIC{$ E(\gamma)$} \dottedLine \RightLabel{D\ref{A:D3}}
\UIC{$ \all \varphi.[\ess{\varphi}{\gamma} \imp \nec \ex x.\varphi(x)] $}\RightLabel{$\all_E$}
\UIC{$ \ess{G}{\gamma} \imp \nec \ex x. G(x) $}\RightLabel{$\imp_E$}
\BIC{$\nec \ex x. G(x)$} \RightLabel{$\imp_I^1$}
\UIC{$\ex z. G(z) \imp \nec \ex x. G(x)$}
\end{prooftree}
\end{small}
%\end{tiny}
\end{proof}

@@

\begin{proof} \hfill
\begin{prooftree}
\AXC{$ $} \RightLabel{2}
\UIC{$\ex z. G(z)$}\RightLabel{$\ex_E$}
\UIC{$G(\gamma)$}  \dottedLine \RightLabel{D\ref{D1}}
\UIC{$\forall \varphi. [P(\lambda x.\varphi(x)) \biimp \nec \varphi(\gamma)]$}\RightLabel{$\forall_E$}
\UIC{$P(G) \biimp \nec G(\gamma)$}
\AXC{Axiom \ref{A:A3}} \RightLabel{}
\UIC{$P(G)$} \RightLabel{$\biimp_E$}
\BIC{$\nec G(\gamma)$}
\AXC{$ $} \RightLabel{1}
\UIC{$G(\gamma)$} \RightLabel{$\ex_I$}
\UIC{$\ex x.G(x)$}  \RightLabel{$\imp_I^1$}
\UIC{$G(\gamma)\imp \ex x.G(x)$} \RightLabel{$\nec_I$}
\UIC{$\nec [G(\gamma)\imp \ex x.G(x)]$} \doubleLine  \RightLabel{(Axiom K)}
\UIC{$\nec G(\gamma)\imp \nec \ex x.G(x)$} \RightLabel{$\imp_E$}
\BIC{$\nec \ex x.G(x)$}\RightLabel{$\imp_I^2$}
\UIC{$\ex z. G(z)\imp \nec \ex x.G(x)$}
\end{prooftree}
%\end{scriptsize}

@@

\begin{small}
\begin{prooftree}
\AXC{Theorem 2}\dashedLine
\UIC{$\all y.[G(y) \imp \ess{G}{y}]$} \RightLabel{D2 }\doubleLine
\UIC{$\all y.[G(y) \imp G(y) \wedge \all \psi. (\nec \psi(y) \biimp \nec \all x. (G(x) \imp \psi(x)))]$}
\UIC{$\all y.[G(y) \imp \all \psi. (\nec \psi(y) \biimp \nec \all x. (G(x) \imp \psi(x)))]$} \doubleLine
%\UIC{$\all y.[G(y) \imp (\nec A(y) \biimp \nec \all x. (G(x) \imp A(x)))]$} \RightLabel{$A$ is constant}
\UIC{$\all y.[G(y) \imp (\nec A \biimp \nec \all x. (G(x) \imp A))]$} \doubleLine
\UIC{$[\subproof_{13}] \qquad \ex y.G(y) \imp (\nec A \biimp \nec \all x. (G(x) \imp A))$}
\end{prooftree}
\end{small}

\begin{small}
\begin{prooftree}
\AXC{$ \subproof_{13} $}\dashedLine
\UIC{$\ex y.G(y) \imp (\nec A \biimp \nec \all x. (G(x) \imp A))$}
\AXC{Theorem 3}\dashedLine
\UIC{$\nec \ex y.G(y)$} \RightLabel{$\nec_E$}
\UIC{$\ex y.G(y)$} \RightLabel{$\imp_E$}
\BIC{$ \nec A \biimp \nec \all x. (G(x) \imp A)$} \doubleLine
\UIC{$ \nec A \biimp \nec (\ex x. G(x) \imp A)$}
\AXC{$ $} \RightLabel{1}
\UIC{$\nec A$} \RightLabel{$\imp_E$}
\BIC{$ \nec (\ex x. G(x) \imp A)$} \RightLabel{$\nec_E$}
\UIC{$ \omega:  \ex x. G(x) \imp A$} %\RightLabel{$\imp_E$}
\AXC{Theorem 3}\dashedLine
\UIC{$\nec \ex y.G(y)$} \RightLabel{$\nec_E$}
\UIC{$\omega: \ex x.G(x)$} \RightLabel{$\imp_E$}
\BIC{$\omega: A$} \RightLabel{$\nec_I$}
\UIC{$ \nec A$} \RightLabel{$\imp_I^1$}
   \UIC{$\nec A\imp \nec A$}
\end{prooftree}
\end{small}

@@

\begin{lemma}
\label{B:L1}
If there is a God-like being, then there is a God-like being necessarily:
$$
\ex z. G_B(z) \imp \nec \ex x. G_B(x)
$$
\end{lemma}
\begin{proof}\hfill
\begin{small}
\begin{prooftree}
\AXC{$ $} \RightLabel{$2$}
\UIC{$G_B(x) $} 
\AXC{$ $}\doubleLine
\UIC{$\nec \all x. [G_B(x) \imp G_B(x)] $}\RightLabel{ D\ref{B:D1}}\dottedLine
\UIC{$P_B(G_B) $}\RightLabel{ $\wedge_I$}
\BIC{$[\subproof_{14}] \qquad G_B(x) \wedge P_B(G_B) $}
\end{prooftree}
\end{small}

\begin{small}
\begin{prooftree}
\AXC{$ \subproof_{14} $}\dashedLine
\UIC{$G_B(x) \wedge P_B(G_B) $}
\AXC{$ $}\RightLabel{ $1$}
\UIC{$(\psi(x) \wedge P_B (\psi))$} \RightLabel{ $\wedge_E$}
\UIC{$P_B (\psi)$}\RightLabel{ D\ref{B:D1}}\dottedLine
\UIC{$\nec\all y.(G_B(y) \imp \psi(y))$} \RightLabel{ $\imp_I^1$}
\UIC{$(\psi(x) \wedge P_B (\psi))\imp \nec\all y.(G_B(y) \imp \psi(y))$}\RightLabel{ $\forall_I$}
\UIC{$\all\psi.((\psi(x) \wedge P_B (\psi)) \imp \nec\all y.(G_B(y) \imp \psi(y)))$} \RightLabel{ $\wedge_I$}
\BIC{$G_B(x) \wedge P_B(G_B) \wedge \all\psi.((\psi(x) \wedge P_B (\psi)) \imp \nec\all y.(G_B(y) \imp \psi(y))) $} \RightLabel{ D\ref{B:D2} }\dottedLine
\UIC{$[\subproof_{15}] \qquad \MCP(G_B, x) $}
